\bf Fast, Scalable Phrase-Based SMT Decoding

### 2016-06-11 acl.2016/amta2016.tex
whatever

%Also, the cube-pruning algorithm contain a priority queue per set of hypotheses sets. This can be independent of how hypotheses are grouped. In the Moses implementation, the priority queue is also attached to the coverage cardinality, Figure~\ref{algo:Cube Pruning with Unsorted Stack}.
%\begin{figure} [h]
%\begin{algorithmic}
%%\REQUIRE source sentence $s$, translation options
%\STATE initialize $queue_{|C|}$
%\FOR{1 to pop-limit}
%  \STATE get best $item$ in $queue_{|C|}$
%  \STATE create hypo from $item$, coverage $C_{new}$
%  \STATE add hypo to $stack_{|C_{new}|}$
%  \STATE create next $items$
%  \STATE add new $items$ to $queue_{|C|}$
%\ENDFOR % { hypothesis in $stack_i$} 
%\end{algorithmic}
%\caption{Cube Pruning with Cardinality Stacks}
%\label{algo:Cube Pruning with Unsorted Stack}
%\end{figure}
%Again, we experiment with diffirent queue configurations, having separate queues for each cardinality, coverage, and coverage \& end position. The stack configuration remained constant (coverage \& end position with pop-limit of 400).
%\begin{table}[h]
%\small
%\begin{center}
%\begin{tabular}{|r|r|r|} \hline
%Queue configuration		& Time		& Score \\ \hline
%Cardinality			& 192		& -8.59922 \\
%Coverage			& 2,413		& -8.58635 \\
%Coverage \& end position	& 7,472		& -8.58263 \\ \hline
%\end{tabular}
%\end{center}
%\caption{Decoding time (in secs with 32 threads) and average model scores for different queue configurations}
%\label{tab:queue-configuration}
%\end{table}
%From the results in Table~\ref{tab:queue-configuration}, using finer grain queues does results in better model scores but it is significantly slower to decode.
% 
We verified that the translation quality of our decoder is comparable to that of Moses in Figure~\ref{fig:bleu}. This fits in with our intention of creating a drop-in replacement for the Moses decoder. 
\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.5]{bleu.png}} 
\end{tabular}
\caption{Translation quality (BLEU) for different pop-limits}
\label{fig:bleu}
\end{figure}

>>>>

%Also, the cube-pruning algorithm contain a priority queue per set of hypotheses sets. This can be independent of how hypotheses are grouped. In the Moses implementation, the priority queue is also attached to the coverage cardinality, Figure~\ref{algo:Cube Pruning with Unsorted Stack}.
%\begin{figure} [h]
%\begin{algorithmic}
%%\REQUIRE source sentence $s$, translation options
%\STATE initialize $queue_{|C|}$
%\FOR{1 to pop-limit}
%  \STATE get best $item$ in $queue_{|C|}$
%  \STATE create hypo from $item$, coverage $C_{new}$
%  \STATE add hypo to $stack_{|C_{new}|}$
%  \STATE create next $items$
%  \STATE add new $items$ to $queue_{|C|}$
%\ENDFOR % { hypothesis in $stack_i$} 
%\end{algorithmic}
%\caption{Cube Pruning with Cardinality Stacks}
%\label{algo:Cube Pruning with Unsorted Stack}
%\end{figure}
%Again, we experiment with diffirent queue configurations, having separate queues for each cardinality, coverage, and coverage \& end position. The stack configuration remained constant (coverage \& end position with pop-limit of 400).
%\begin{table}[h]
%\small
%\begin{center}
%\begin{tabular}{|r|r|r|} \hline
%Queue configuration		& Time		& Score \\ \hline
%Cardinality			& 192		& -8.59922 \\
%Coverage			& 2,413		& -8.58635 \\
%Coverage \& end position	& 7,472		& -8.58263 \\ \hline
%\end{tabular}
%\end{center}
%\caption{Decoding time (in secs with 32 threads) and average model scores for different queue configurations}
%\label{tab:queue-configuration}
%\end{table}
%From the results in Table~\ref{tab:queue-configuration}, using finer grain queues does results in better model scores but it is significantly slower to decode.
% 
We verified that the translation quality of our decoder is comparable to that of Moses in Figure~\ref{fig:bleu}, given the same parameters and models. This fits in with our intention of creating a drop-in replacement for the Moses decoder. 
\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.5]{bleu.png}} 
\end{tabular}
\caption{Translation quality for different pop-limits}
\label{fig:bleu}
\end{figure}
